Constraint Programming - Inside Gecode

### 2014-05-02 paper.tex
added figure for squares

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{cite}
\usepackage{amsfonts}
\usepackage[pdftex]{graphicx}
\graphicspath{{../png/}}
\DeclareGraphicsExtensions{.png}
\usepackage[cmex10]{amsmath}
\interdisplaylinepenalty=2500
\usepackage{algorithmic}
\usepackage{array}
\usepackage{mdwmath}
\usepackage{mdwtab}
\usepackage{eqparbox}
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage{fixltx2e}
\usepackage{stfloats}
\usepackage{url}
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage{listings}
\usepackage{color}

@@

	\subsection{Constraint Types}
	As already mentioned before constraint programming is the generalization of linear programming, therefore it is at least possible do define linear constraints like \ref{eq:linearConstraint}. Which statements are possible to make varies than very much from the programming language in which the problem is implemented and the used toolset. Typical constraints would be
	\begin{itemize}
		\item Equalities: $x = y + 2$, $x^2 + y^2 = 1$, \dots
		\item Inequalities: $x \ne y$, \dots
		\item Relations: $x < 2 y$, $e^x < 4$, \dots
	\end{itemize}
	In Gecode for example it is very easy to create for example a nonlinear constraint based on the integer variables a, b, c and d \cite[p. 120]{programmingGecode}:
	\begin{lstlisting}
rel(home, a+b*(c+d) == 0);
	\end{lstlisting}
	This single statement in C++ implements the constraint
	\begin{equation}
		a + b \cdot (c + d) == 0
	\end{equation}
	what is a quite handy way to do it.

	Hence there are boolean variables available it is also possible to use logical operators to combine other constraint types to logical expressions. To show the usage of this on an example I will give the implementation for the placement of two squares such that they do not overlap. This problem can be expressed mathematically by \cite[p. 101]{programmingGecode}
	\begin{equation}
	\begin{split}
		x_1 + d_1 \le x_2 & \lor x_2 + d_2 \le x_1 \lor \\
		y_1 + d_1 \le y_2 & \lor y_2 + d_2 \le y_1
	\end{split}
	\end{equation}
	and in Gecode by
	\begin{lstlisting}
rel(home,	(x1 + d1 <= x2) || 
		(x2 + d2 <= x1) || 
		(y1 + d1 <= y2) || 
		(y2 + d2 <= y1));
	\end{lstlisting}
	which is again quite obvious to a reader with some experience in a C-like programming language.

>>>>

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{cite}
\usepackage{amsfonts}
\usepackage[pdftex]{graphicx}
\graphicspath{{../png/}}
\DeclareGraphicsExtensions{.png}
\usepackage[cmex10]{amsmath}
\interdisplaylinepenalty=2500
\usepackage{algorithmic}
\usepackage{array}
\usepackage{mdwmath}
\usepackage{mdwtab}
\usepackage{eqparbox}
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage{fixltx2e}
\usepackage{stfloats}
\usepackage{url}
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage{tikz}
\usepackage{listings}
\usepackage{color}

@@

	\subsection{Constraint Types}
	As already mentioned before constraint programming is the generalization of linear programming, therefore it is at least possible do define linear constraints like [equation \ref{eq:linearConstraint}]. Which statements are possible to make varies than very much from the programming language in which the problem is implemented and the used toolset. Typical constraints would be
	\begin{itemize}
		\item Equalities: $x = y + 2$, $x^2 + y^2 = 1$, \dots
		\item Inequalities: $x \ne y$, \dots
		\item Relations: $x < 2 y$, $e^x < 4$, \dots
	\end{itemize}
	In Gecode for example it is very easy to create for example a nonlinear constraint based on the integer variables a, b, c and d \cite[p. 120]{programmingGecode}:
	\begin{lstlisting}
rel(home, a+b*(c+d) == 0);
	\end{lstlisting}
	This single statement in C++ implements the constraint
	\begin{equation}
		a + b \cdot (c + d) == 0
	\end{equation}
	what is a quite handy way to do it.

	\begin{figure}
	\center
	\begin{tikzpicture}
		\draw (0, 0) rectangle (1, 1);
		\node at (0, -0.3) {($x_1$, $y_1$)};
		\draw[arrows=<->] (1.2, 0) -- (1.2, 1);
		\node at (1.5, 0.5) {$d_1$};
		\draw (1.5, 1.5) rectangle(2, 2);
		\node at (1.5, 1.2) {($x_2$, $y_2$)};
		\draw[arrows=<->] (2.2, 1.5) -- (2.2, 2);
		\node at (2.5, 1.75) {$d_2$};
	\end{tikzpicture}
	\caption{two squares which should not overlap}
	\label{fig:squares}
	\end{figure}
	Hence there are boolean variables available it is also possible to use logical operators to combine other constraint types to logical expressions. To show the usage of this on an example I will give the implementation for the placement of two squares such that they do not overlap [figure \ref{fig:squares}]. This problem can be expressed mathematically by \cite[p. 101]{programmingGecode}
	\begin{equation}
	\begin{split}
		x_1 + d_1 \le x_2 & \lor x_2 + d_2 \le x_1 \lor \\
		y_1 + d_1 \le y_2 & \lor y_2 + d_2 \le y_1
	\end{split}
	\end{equation}
	and in Gecode by
	\begin{lstlisting}
rel(home,	(x1 + d1 <= x2) || 
		(x2 + d2 <= x1) || 
		(y1 + d1 <= y2) || 
		(y2 + d2 <= y1));
	\end{lstlisting}
	which is again quite obvious to a reader with some experience in a C-like programming language.
